\section{Background}
\textbf{Architecture.}
Embedded systems span a wide range of platforms, from resource-constrained microcontrollers to heterogeneous FPGA-based systems-on-chip.
This project focuses on two representative classes: FPGA SoCs and Arm Cortex-M-based systems.
An FPGA SoC integrates a fixed processor subsystem with programmable logic connected through on-chip interconnects.
The processor subsystem typically executes system software and manages external memory, while the programmable logic can be configured with soft-core processors, local block RAM, peripherals, and communication modules.
Cortex-M-based systems range from single-core microcontrollers to multicore and heterogeneous SoCs and commonly execute bare-metal firmware or lightweight RTOS workloads.
Cortex-M processors provide \textit{Thread} mode for normal software execution and \textit{Handler} mode for exceptions and interrupts.
They support privileged and unprivileged execution and include general-purpose registers, including stack-pointer registers, as well as system registers for managing processor state and configuration.
Recent Cortex-M architectures also incorporate security features such as TrustZone, memory protection units (MPUs), and hardware cryptographic support.

\textbf{Trusted Execution Environments.}
Trusted execution environments (TEEs) use hardware-enforced isolation to protect security-sensitive code and data from the rest of the system.
An embedded TEE typically separates execution into a trusted domain and a general-purpose or untrusted domain, with controlled interfaces governing communication across the security boundary.
The trusted domain may host cryptographic services and secure storage, while the untrusted domain executes the remaining firmware or operating-system software.
On Cortex-M processors, TrustZone enforces this separation through controlled transitions using designated entry points, security-aware control-transfer instructions (i.e., \texttt{SG}, \texttt{BLNS}), and protected exception handling.
FPGA SoCs commonly integrate hard-core processors, such as Arm Cortex-A or RISC-V cores, which may provide their own TEE support.
Their programmable logic can also be configured with soft-core processors, and interconnects to construct additional execution domains.
Although TEEs provide a foundation for trusted execution, their security depends on the correctness of the trusted software and the integrity of the hardware resources and configurations that enforce the isolation boundary.